\chapter{Network packets}\label{app:network}

The final format of the network packages are described in this appendix.
For all packages, it is assumed that the TCP messages are treated as unicast to a single recipient, and UDP messages are treated as multicast.
All of these packets will only describe the actual data of the packet, and not contain the UDP/TCP headers.
Each packet contains an ID identifying the type as well as the required information.
Additionally, each TCP package will be prefixed with a number indicating the length of the current message, since it is transmitted as a stream. 
This ensures that the receiver knows when to stop reading the current packet and be ready to process the next one.


\section*{0: Send tag position (UDP)}
\begin{table}[H]
\begin{tabular}{|l|l|l|l|l|}
\hline
\textbf{POSY (y)} & \textbf{POSX (x)} & \textbf{ID (i)} & \textbf{TIMESTAMP (s)} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}TYPE (t)\\ 0\end{tabular}}} \\ \hline
16 bit            & 16 bit            & 8 bit           & 8 bit                  & 8 bit                                                                              \\ \hline
\end{tabular}
\end{table}

Purpose: The position of a given tag will be continuously transmitted on the multicast channel for all players to receive.
The positions are sent as values relative to the anchor positions sent during setup, such that a missed package will not impact the future game state.
The ID (i) \texttt{0} is reserved for the ball tag, and all other tags are considered to be players.
For a game with 4 players, each would have a unique ID ranging from 1-4.


\section*{1: Send anchor position (TCP)}
\begin{table}[H]
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{POSY (y)} & \textbf{POSX (x)} & \textbf{ANCHOR\_ID (i)} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}TYPE (t)\\ 1\end{tabular}}} \\ \hline
16 bit            & 16 bit            & 8 bit                   & 8 bit                                                                              \\ \hline
\end{tabular}
\end{table}

Purpose: Used as a part of the setup phase, where the host sends the position of one of the four anchors to the player.
This packet will be sent multiple times to each client, but with various anchor IDs (i) until all clients have received the four positions.

\section*{2: Send player tag (TCP)}
\begin{table}[H]
\begin{tabular}{|l|l|l|}
\hline
\textbf{PLAYER\_ID (p)} & \textbf{TAG\_ID (i)} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}TYPE (t)\\ 2\end{tabular}}} \\ \hline
8 bit                   & 16 bit               & 8 bit                                                                              \\ \hline
\end{tabular}
\end{table}
Purpose: Used as a part of the setup phase, where the host sends the related tag ID to the player, such that they can find the physical tag related to their client instance.
This packet will be sent once to each client, but with various tag IDs (i) until all clients have received their tag ID.

\section*{3: Signal game start (TCP)}
\begin{table}[H]
\begin{tabular}{|l|}
\hline
\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}TYPE (t)\\ 3\end{tabular}}} \\ \hline
8 bit                                                                               \\ \hline
\end{tabular}
\end{table}

Purpose: Used to signal to the players that the game has been started.

\section*{4: Send goal scored (TCP)}
\begin{table}[H]
\begin{tabular}{|l|l|l|}
\hline
\textbf{TEAM2SCORE (2)} & \textbf{TEAM1SCORE (1)} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}TYPE (t)\\ 4\end{tabular}}} \\ \hline
8 bit                   & 8 bit                   & 8 bit                                                                              \\ \hline
\end{tabular}
\end{table}

Purpose: Used to signal the clients that a goal has been scored, and the scoreboard should be updated on their GUI.
This triggers the host to generate new goal positions.

\section*{5: Send new goal position (TCP)}
\begin{table}[H]
\begin{tabular}{|l|l|l|l|l|}
\hline
\textbf{Offset (o)} & \textbf{POSY (y)} & \textbf{POSX (x)} & \textbf{TEAM\_ID (i)} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}TYPE (t)\\ 5\end{tabular}}} \\ \hline
8 bit & 16 bit            & 16 bit            & 8 bit                 & 8 bit                                                                              \\ \hline
\end{tabular}
\end{table}

Purpose: Sends a new goal position to the clients.
This message will be sent twice to each team when a goal is scored, such that they receive new positions for both teams' goals.
The positions are the X and Y coordinates of the center of the goal as they have a pre-defined size based on the shortest edge of the playing field.
It also contains the offset of goal zones (o), which is the distance from the center of the goal to the sides of the goal.

\section*{6: Send player and goal amounts (TCP)}
\begin{table}[H]
\begin{tabular}{|l|l|l|}
\hline
\textbf{PLAYERNUMBER (n)} & \textbf{GOALNUMBER (n)} & \multicolumn{1}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}TYPE (t)\\ 6\end{tabular}}} \\ \hline
8 bit                   & 8 bit                   & 8 bit                                                                              \\ \hline
\end{tabular}
\end{table}

Purpose: Sends the host defined information relating to number of players and goals needed to win.

\section*{7: Signal game end (TCP)}
\begin{table}[H]
\begin{tabular}{|l|}
\hline
\multicolumn{1}{|c|}{\textbf{\begin{tabular}[c]{@{}c@{}}TYPE (t)\\ 7\end{tabular}}} \\ \hline
8 bit                                                                               \\ \hline
\end{tabular}
\end{table}

Purpose: Used to signal to the players that the game has ended.