\chapter{Conclusion}\label{chap:conclusion}
This chapter presents the conclusion of the project and the work that was done during the semester.
As mentioned in \autoref{sec:projectidea}, the initial project idea was to build a location-based game using virtual reality.\\
\\
As a result of using the Essence approach for the project, this idea was continuously developed upon and resulted in a slightly different project than first envisioned.
The report reflects how these ideas evolved and which pivots happened along the way.
Essence was interesting to try as a process model, but it is doubtful whether it will be used in future projects instead of a regular agile approach, as discussed in \autoref{evaluationessence}.
\\
The result of the project work was a working VR game which was tested through an evaluation test.
Several requirements were defined in \autoref{sec:mvp} comprising an MVP.
These requirements were achieved as discussed in \autoref{sec:discussmvp}.
The evaluation test was used to successfully discover bugs, but the preparation for the first test was not adequate as discussed in \autoref{discussevaluations}.
\\
Section \ref{sec:final-design} compared the final design to that which was defined through prototypes in \autoref{sec:sprint1-prototypes}.
The design was determined to accomplish the initial goals, but it lacks a lobby feature to be used instead of manually typing the IP of the host every time a player wants to join.
\\\\
Mobility was an important aspect of the project, as defined in \autoref{sec:mobility}, and as discussed in \autoref{sec:mobility-reflection}, this system achieves the aim of being mobile.
\\\\
The results of the project work show that while Pozyx provides high accuracy, the refresh rate that we were able to achieve using it was not fast enough for a real-time experience.
It is concluded that combining Pozyx with a technique like dead reckoning would possibly improve the experience.
\\
Additionally, \autoref{discuss:futurework} suggests some ideas that could be implemented in the future to improve the game, such as powerups, having a virtual ball and allowing the players to see which direction they are currently facing.
