\section{Process changes}
The process required some unexpected pivots in the second sprint due to the coronavirus, which lead to the university being locked down for a period.
\\
The daily group work was moved from the physical group room to a virtual setting facilitated by Discord.
One of the major differences was that it was previously possible to sit down and do the pair reviews in the morning, which meant that they would go through review quickly.
However, while we tried to still get the pair reviews done first thing in the morning, there was a noticeable delay before the new features were reviewed and merged.\\
Another minor change was how we assigned points (cost, reward, priority) to tasks. This worked out well with online, as people could simultaneously post their point number in a chat, as opposed to showing a number of fingers while sitting around a table.

Since most of the project work is managed on Jira and completed by individual group members, there was not a noticeable change in the amount of work getting done.
A slight side effect of working with only voice chat has been that it was occasionally difficult to reach the other members when their help was needed since they might be temporarily away from the computer, or too distracted or focused to be paying attention to the voice chat.
This also resulted in some information not getting spread to the entire group, as not everyone may have been listening in while some discussion was happening, which lead to minor confusion in further discussions on the subject.
